\begin{thebibliography}{}

\bibitem[\protect\citename{The Milwaukee Sentinel}1926]{The Milwaukee Sentinel:26}
The Milwaukee Sentinel.
\newblock 1926-12-08.
\newblock {\em 'Phantom Auto' Will Tour City}.
\newblock Google News Archive.
% TODO: Supress error \newblock \href{https://news.google.com/newspapers?id=unBQAAAAIBAJ&sjid=QQ8EAAAAIBAJ&pg=7304,3766749}{https://news.google.com/newspapers?id=unBQAAAAIBAJ&sjid=QQ8EAAAAIBAJ&pg=7304,3766749}

\bibitem[\protect\citename{S. Thrun \bgroup et al. \egroup}2006]{Thrun:06}
Sebastian Thrun, Mike Montemerlo, Hendrik Dahlkamp, David Stavens, Andrei Aron, James Diebel, Philip Fong, John Gale, Morgan Halpenny, Gabriel Hoffmann, Kenny Lau, Celia Oakley, Mark Palatucci, Vaughan Pratt, Pascal Stang, Sven Strohband, Cedric Dupont, Lars-Erik Jendrossek, Christian Koelen, Charles Markey, Carlo Rummel, Joe van Niekerk, Eric Jensen, Philippe Alessandrini, Gary Bradski, Bob Davies, Scott Ettinger, Adrian Kaehler, Ara Nefian and Pamela Mahoney.
\newblock 2006.
\newblock {\em Stanley: The robot that won the DARPA Grand Challenge}.
\newblock Journal of Field Robotics, volume 23, issue 9.

\bibitem[\protect\citename{The Press-Courier}1960]{Press-Courier:60}
Doc Quigg
\newblock 1960-06-07.
\newblock {\em Reporter Rides Driverless Car}.
\newblock Google News Archive.
% TODO: Supress error \newblock \href{https://news.google.com/newspapers?id=vUpeAAAAIBAJ&sjid=3WANAAAAIBAJ&pg=6885,3667738&hl=en}{https://news.google.com/newspapers?id=vUpeAAAAIBAJ&sjid=3WANAAAAIBAJ&pg=6885,3667738&hl=en}

\bibitem[\protect\citename{B. Schweber}]{Mouser}
Bill Schweber.
\newblock {\em The Autonomous Car: A Diverse Array of Sensors Drives Navigation, Driving, and Performance}.
\newblock Mouser Electronics.
\newblock \href{http://eu.mouser.com/applications/autonomous-car-sensors-drive-performance/}{http://eu.mouser.com/applications/autonomous-car-sensors-drive-performance/}

\bibitem[\protect\citename{T. Hellstr\"{o}m} 2009]{Umea:09}
Thomas Hellstr\"{o}m
\newblock 2009.
\newblock {\em Sensors for autonomous vehicles}.
\newblock Ume{\aa} University.
\newblock
\href{http://www8.cs.umu.se/kurser/5DV029/HT09/handouts/Sensors for autonomous vehicles .pdf}{http://www8.cs.umu.se/kurser/5DV029/HT09/handouts/Sensors for autonomous vehicles .pdf}

\bibitem[\protect\citename{EIJ} 2012]{EIJ:12}
Earth Imaging Journal
\newblock 2012-01-24.
\newblock {\em LiDAR Boosts Brain Power for Self-Driving Cars}.
\newblock Earth Imaging Journal.
\newblock
\href{http://eijournal.com/resources/lidar-solutions-showcase/lidar-boosts-brain-power-for-self-driving-cars}{http://eijournal.com/resources/lidar-solutions-showcase/lidar-boosts-brain-power-for-self-driving-cars}


\bibitem[\protect\citename{C. Squatriglia} 2012]{Squatriglia:10}
Chuck Squatriglia
\newblock 2010-11-19.
\newblock {\em Audi's Robotic Car Climbs Pikes Peak}.
\newblock Wired.
\newblock
\href{http://www.wired.com/2010/11/audis-robotic-car-climbs-pikes-peak/}{http://www.wired.com/2010/11/audis-robotic-car-climbs-pikes-peak/}

\bibitem[\protect\citename{P. Beeson} 2009]{Beeson:09}
Patrick Beeson
\newblock 2009.
\newblock {\em Autonomous Vehicles - Lesson 2: Location Sensing}.
\newblock University of Texas.
\newblock
\href{https://www.cs.utexas.edu/~pstone/Courses/393Rfall09/resources/sensing.pdf}{https://www.cs.utexas.edu/{\texttildelow}pstone/Courses/393Rfall09/resources/sensing.pdf}

\bibitem[\protect\citename{A. Davies} 2015]{Davies:15}
Alex Davies
\newblock 2015-04-22.
\newblock {\em Turns Out the Hardware in Self-Driving Cars Is Pretty Cheap}.
\newblock Wired.
\newblock
\href{http://www.wired.com/2015/04/cost-of-sensors-autonomous-cars/}{http://www.wired.com/2015/04/cost-of-sensors-autonomous-cars/}

\bibitem[\protect\citename{A. Iliaifar} 2013]{Iliaifar:13}
Amir Iliaifar
\newblock 2013-02-06.
\newblock {\em LIDAR, lasers, and logic: Anatomy of an autonomous vehicle}.
\newblock Digital Trends.
\newblock
\href{http://www.digitaltrends.com/cars/lidar-lasers-and-beefed-up-computers-the-intricate-anatomy-of-an-autonomous-vehicle/}{http://www.digitaltrends.com/cars/lidar-lasers-and-beefed-up-computers-the-intricate-anatomy-of-an-autonomous-vehicle/}

\end{thebibliography}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
